Simple Test coexistence

### 2018-06-05 first_simultations.Rmd
Second file added. Env_curve renamed and width parameter.

```{r}
devtools::load_all()
#### Keep stable for all
patches  <- 25   # Number of patches
species  <- 25   # Number of species
time     <- 150	 # Length of model run (generations)
initpop  <- 50   # initial population size
n_traits <- 1    # number of traits
k        <- 1.45 # Niche height
c        <- 10 # Niche breadth

@@

## Single Trait Competition
trait_type = c(trait1 = "A")
single_trait_compet = multigen(traits = traits, trait_type = trait_type,
                               env = env, time = time, species = species,
                               patches = patches, composition = composition,
                               A = A, d = d, k = k, c = c)
single_trait_compet_final = ifelse(single_trait_compet$compo[,,time] < 2, 0, single_trait_compet$compo[,,time])

## Single Trait Growth
trait_type = c(trait1 = "R")
single_trait_growth = multigen(traits = traits, trait_type = trait_type,
                               env = env, time = time, species = species,
                               patches = patches, composition = composition,
                               A = A, d = d, k = k, c = c)
single_trait_growth_final = ifelse(single_trait_growth$compo[,,time] < 2, 0,
                                   single_trait_growth$compo[,,time])

## Both
trait_type = c(trait1 = "RA")
single_trait_both = multigen(traits = traits, trait_type = trait_type,
                             env = env, time = time, species = species,
                             patches = patches, composition = composition,
                             A = A, d = d, k = k, c = c)

@@

devtools::load_all()
#### Keep stable for all
patches  <- 25   # Number of patches
species  <- 25   # Number of species
time     <- 150	 # Length of model run (generations)
initpop  <- 50   # initial population size
n_traits <- 1    # number of traits
k        <- 1.45 # Niche height
c        <- 10 # Niche breadth

@@

two_traits <- apply(trait_types, 1,
                    function(x){
                        two_traits_types = multigen(traits = traits, trait_type = x,
                                                    env = env, time = time, species = species,
                                                    patches = patches, composition = composition,
                                                    A = A, d = d, k = k, c = c)
                    })
names(two_traits) <- paste(trait_types[, 1], trait_types[, 2], sep = "_")

>>>>

```{r}
devtools::load_all()
#### Keep stable for all
patches  <- 25   # Number of patches
species  <- 25   # Number of species
time     <- 150	 # Length of model run (generations)
initpop  <- 50   # initial population size
n_traits <- 1    # number of traits
k        <- 1.45 # Niche height
width    <- 10 # Niche breadth

@@

## Single Trait Competition
trait_type = c(trait1 = "A")
single_trait_compet = multigen(traits = traits, trait_type = trait_type,
                               env = env, time = time, species = species,
                               patches = patches, composition = composition,
                               A = A, d = d, k = k, width = width)
single_trait_compet_final = ifelse(single_trait_compet$compo[,,time] < 2, 0, single_trait_compet$compo[,,time])

## Single Trait Growth
trait_type = c(trait1 = "R")
single_trait_growth = multigen(traits = traits, trait_type = trait_type,
                               env = env, time = time, species = species,
                               patches = patches, composition = composition,
                               A = A, d = d, k = k, width = width)
single_trait_growth_final = ifelse(single_trait_growth$compo[,,time] < 2, 0,
                                   single_trait_growth$compo[,,time])

## Both
trait_type = c(trait1 = "RA")
single_trait_both = multigen(traits = traits, trait_type = trait_type,
                             env = env, time = time, species = species,
                             patches = patches, composition = composition,
                             A = A, d = d, k = k, width = width)

@@

devtools::load_all()
#### Keep stable for all
patches  <- 25   # Number of patches
species  <- 25   # Number of species
time     <- 150	 # Length of model run (generations)
initpop  <- 50   # initial population size
n_traits <- 1    # number of traits
k        <- 1.45 # Niche height
width    <- 10 # Niche breadth

@@

two_traits <- apply(trait_types, 1,
                    function(x){
                        two_traits_types = multigen(traits = traits, trait_type = x,
                                                    env = env, time = time, species = species,
                                                    patches = patches, composition = composition,
                                                    A = A, d = d, k = k, width = width)
                    })
names(two_traits) <- paste(trait_types[, 1], trait_types[, 2], sep = "_")
